---
title: "Perception of Baybaynons on local food industry in Baybay City: an input to gastronomic tourism"
author: "ViSERDAC"
date: last-modified
format: 
  html:
    css: custom.scss
    self-contained: true
    mainfont: arial
    fontsize: 1em
    linestretch: 1.5
    toc: true
    toc-location: left
    toc-depth: 3
    number-sections: true
    code-fold: true
    theme:
      light: cosmo
      dark: darkly
execute:
  message: false
  warning: false
  fig-align: center
editor: visual
---

```{r}
#| echo: false
#| message: false
#| warning: false

# set working directory
setwd(here::here("laurente-baybay-local-foods"))

# libraries
library(tidyverse)
library(readxl)
library(janitor)
library(scales)


# data management source
source("data-management.R")

# custom theme
custom_theme <- 
  theme_set(theme_minimal()) +
  theme(plot.title = element_text(hjust = 0.5, size = 16, margin = margin(b=20), face = "bold"),
        plot.margin = margin(t = 20, r = 20, b = 20, l = 20),
        panel.grid = element_blank(),
        axis.text = element_text(size = 12),
        legend.position = "bottom",
        strip.text = element_text(size = 14))


```

# Attachment

# Objective 1: To describe the socio-demogprahic profile of the respondents

# Objective 2: To measure the level of awareness of the Baybayanons.

## Rice-based delicacies

```{r}
p_aware_rice <- 
    aware_rice_based_dta |> 
    ggplot(aes(pct, delicacy, fill = rate_lab)) +
    geom_col() +
    geom_text(aes(label = pct_lab), position = position_fill(vjust = 0.5), color = "white", fontface = "bold") +
    scale_fill_manual(values = c("#073b4c", "#118ab2", "#06d6a0", "#ffba66ff", "#e63946")) +
    scale_x_continuous(labels = percent_format()) +
    custom_theme +
    labs(
    title = "Rice-based delicacies level of awareness",
    fill =  NULL,
    y = NULL,
    x = NULL
    )

ggsave(
    plot = p_aware_rice,
    filename = "plot/aware_rice.jpg",
    dpi = 400,
    unit = "in",
    width = 8,
    height = 6
)

```

## Snacks and processed products

```{r}
## plotting awareness for snacks and processed foods
p_snack_processed <- 
    aware_snacks_process_dta |> 
    ggplot(aes(pct, delicacy, fill = rate_lab)) +
    geom_col() +
    geom_text(aes(label = pct_lab), position = position_fill(vjust = 0.5), color = "white", fontface = "bold") +
    scale_fill_manual(values = c("#073b4c", "#118ab2", "#06d6a0", "#ffba66ff", "#e63946")) +
    scale_x_continuous(labels = percent_format()) +
    custom_theme +
    labs(
    title = "Snacks and processed products level of awareness",
    fill =  NULL,
    y = NULL,
    x = NULL
    )

ggsave(
    plot = p_snack_processed,
    filename = "plot/aware_snacks_processed.jpg",
    dpi = 400,
    unit = "in",
    width = 8,
    height = 6
)
```


## Beverage, dairy and specialty products

```{r}
## plotting beverage, dairy and specialty products
p_aware_beverage_dairy <- 
    aware_beverage_dairy_dta |> 
    ggplot(aes(pct, delicacy, fill = rate_lab)) +
    geom_col() +
    geom_text(aes(label = pct_lab), position = position_fill(vjust = 0.5), color = "white", fontface = "bold") +
    scale_fill_manual(values = c("#073b4c", "#118ab2", "#06d6a0", "#ffba66ff", "#e63946")) +
    scale_x_continuous(labels = percent_format()) +
    custom_theme +
    labs(
    title = "Beverage, dairy, and specialty products level of awareness",
    fill =  NULL,
    y = NULL,
    x = NULL
    )

ggsave(
    plot = p_aware_beverage_dairy,
    filename = "plot/aware_beverage_dairy.jpg",
    dpi = 400,
    unit = "in",
    width = 8,
    height = 5
)
```


















# Objective 3: To measure the resident's perception of local delicacies in terms of product marketability, cuisine prepservation.

# Objective 4: To assess the residents' willingness to support towards gastronomic tourism.

# Objective 5: To support for gastronomic tourism thorugh policy recommendation.


