---
title: "Level of awareness and perceived impact of Artificial Intelligence (AI) in academic activities among graduate students of Visayas State University"
subtitle: "Client: Sato Rintaro"
date: last-modified
format: 
  html:
    css: custom.scss
    self-contained: true
    mainfont: arial
    fontsize: 1em
    linestretch: 1.5
    toc: true
    toc-location: left
    toc-depth: 3
    number-sections: true
    code-fold: true
    theme:
      light: cosmo
      dark: darkly
execute:
  message: false
  warning: false
  fig-align: center
editor: visual
---

```{r}
#| echo: false
#| message: false
#| warning: false
# set working directory
setwd(here::here("rentaro-ai-effects-academic"))

# libraries
library(tidyverse)
library(readxl)
library(janitor)
library(scales)
library(EFAtools)
library(psych)
library(seminr)
library(gtsummary)
library(kableExtra)
library(correlation)
library(reshape2)


# data management source
source("data-management.R")
```

# Attachments

::: callout-note
Copies of the Figures presented in this report are available using the links below. All the files can be accessed in the Google drive folder.
:::

<ol>

<li><a href="" target="_blank" style="text-decoration: none">Plots</a></li>

<li><a href="" target="_blank" style="text-decoration: none">Google Drive</a></li>

</ol>

# Objective 1: Determine the level of graduate students' awareness of AI tools used in academic activities.

# Objective 2: Describe the levels of performance expectancy, effort expectancy, and ethical risk perception as component of overall AI perception.

# Objective 4: Assess the extent of graduate students' AI usage behavior in their academic activities.

# Objective 5: Examine the influence of awareness of AI tools on overall AI perception.

# Objective 6: Determin the effects of overall AI perception on AI usage behvior.

# Objective 7: Examine whether socio-demographic characteristics are associated with awareness of AI perception, and AI usage behvior.

# Objective 8: Describe characteristics of respondents towards AI.

```{r}
## descriptive
ai_ms_dta |>
  select(age:ai_tools_used) |>
  select(
    -c(
      weekly_allowance,
      working_experience,
      residence,
      major,
      degree,
      gadget_own,
      gadget_own_type,
      internet_source,
      internet_provider,
      internet_monthly_budget,
      ai_info_source,
      ai_training,
      ai_tools_used
    )
  ) |>
  tbl_summary(
    statistic = list(all_categorical() ~ "{n} ({p}%)"),
    missing = "no",
    label = list(
      age ~ "Age",
      sex ~ "Gender",
      program ~ "Program",
      year_level ~ "Year Level",
      grad_years ~ "Years in Graduate School",
      employment_status ~ "Employment Status",
      internet_availability ~ "Internet
      Availability",
      ai_familiarity ~ "Familiarity with AI",
      ai_use_freq ~ "Frequency of AI Use"
    )
  ) |>
  bold_labels() %>%
  as_kable_extra(linesep = "") %>%
  kable_minimal() %>%
  kable_styling(
    full_width = F,
    fixed_thead = T,
    bootstrap_options = c("striped", "hover", "condensed", "responsive")
  )
```